\documentclass{article}

\usepackage{titlesec}
\usepackage{titling}
\usepackage[margin=1in]{geometry}
\usepackage{tabto}
\titleformat{\section}
{}
{}
{.25em}
{\filcenter\huge\bfseries}[\titlerule]

\titleformat{\subsection}
{\bfseries\Large}{\hspace{-.25in}}{1em}{}

\titleformat{\subsubsection}
{\bfseries}
{}
{0em}
{}[]


\renewcommand{\maketitle}{
\begin{center}
{\huge\bfseries
\theauthor}
\vspace{.25em}

Apt \#8 \#9 Henry Street, Gasparillo

salahuddeen.ahmed@outlook.com

https://github.com/Salahuddeen


\end{center}
}

\titlespacing{\subsection}
{1em}{.25em}{0em}



\begin{document}
\author{Salahuddeen Ahmed}

\maketitle

\section {Education}
\subsection{Undergraduate}
Bsc. Information Technology (Special) \hfill{2015-2018}

\hspace{10mm}University of the West Indies

\subsection{Secondary}
CAPE Examinations \hfill {2012-2014}

\hspace{10mm} Presentation College San Fernando

CXC Examinations \hfill {2008-2012}

\hspace{10mm}A.S.J.A. Boys College San Fernando
\section{Technical skills}

\subsection{Programming}
Python, HTML, CSS, Javascript, Java, Bash, Batch, Visual Basic, SQL

\subsection{Markup}
{\LaTeX}, HTML, CSS

\section{Programming Experience}

\subsubsection{Matrix of U App \hfill{2018}} 
{\bfseries Description:} Responsive web application that allows registered users to store medical information that is accessible by hospital personnel.
\\{\bfseries Technologies:} Django, Python, HTML, CSS, Javascript, Bootstrap 4, SQLite

\subsubsection{UWI E-Advisor \hfill{2018}}
{\bfseries Description:} Responsive web application that allows students go get advising information for the current semester based on their completed courses and degree program. 
\\{\bfseries Technologies:} Django, Python, HTML, CSS, Javascript, Bootstrap 4, MySQL

\subsubsection{Hackathon \hfill{2017}}
{\bfseries Description:} Comminity garden management and administration application. Allows users to collect donations, manage and locate community gardens. 
\\{\bfseries Technologies:} HTML, CSS, Javascript, Firebase, Google Maps API, Bootstrap 4

\subsubsection{UWICoin \hfill{2017}}
{\bfseries Description:} Conceptual design of an application that allows cashless transactions across the University campus. Did not include implementation of project.
\\{\bfseries Technologies:} Visio, Microsoft Project, Microsoft Project. 


\section{Achievements}
\subsubsection{Subject Prize English \hfill{2012}}
\tab Awarded for profiency in English language in the CSEC Examinations
\subsubsection{Subject Prize Social Studies \hfill{2012}}
\tab Awarded for profiency in Scoial Studies in the CSEC Examinations
\subsubsection{Principal's Award \hfill{2012}}
\tab Awarded for upholding college ideals and leadership.
\subsubsection{School Prefect \hfill{2011}}
\tab Assist in management and supervision of students at the college.
\subsubsection{Certification in Basic First Aid and CPR \hfill{2011}}
\tab Red Cross First Aid Certification 
\subsubsection{School Prefect \hfill{2010}}
\tab Awarded for profiency and excellent performance in scouting activities.

\section{Interest/Activities}
\begin{itemize}
	\item Member of the 3rd A.S.J.A. Sea Scouts.
 	\item Cricket
	\item Football
	\item Sailing
	\item UWICS (University of the West Indies Computing Society)
	\item UWIIS (University of the West Indies Islamic Society)	
\end{itemize}

\section{Personal Skills}
\begin{itemize}
	\item Honest and Reliable
	\item Flexible
	\item Capable Driver
	\item Good Time Management
	\item Always seeking self improvement
	\item Good work ethic
\end{itemize}
\end{document}
